Stage-Splitting a Modal Language

### 2014-09-30 paper/semantics.tex
made comments about prev reduction more explicit

More precisely, when evaluating the \verb|next|, we construct an explicit
substitution $\mathtt{[\hat y\mapsto f~20]}$ binding its old contents to the
fresh variable $\mathtt{\hat y}$. This substitution is placed at the top of the
containing $\prev$ block:
\begin{lstlisting} 
prev {
[yhat|->f 20]
  let x = (next{yhat}, 7) in
  next{prev{#1 x} * prev{#1 x} *  hold{#2 x}}
}
\end{lstlisting}
%As a convention, we render the new variable with a %stylish and fashionable
%hat.  
We proceed with stage~\bbone\ evaluation, which now duplicates the variable
$\mathtt{\hat y}$ rather than the expression \verb|f 20|.
\begin{lstlisting} 
prev {
[yhat|->f 20]
  next{
    prev{#1 (next {yhat}, 7)} * 
    prev{#1 (next {yhat}, 7)} *
    hold{#2 (next {yhat}, 7)}
  }
}
\end{lstlisting}
We then speculate and reduce the projections to get:
\begin{lstlisting} 
prev {
[yhat|->f 20]
    next{ yhat * yhat * 7 }
}
\end{lstlisting}
Once again, we lift the contents of the $\next$ into a substitution:
\begin{lstlisting} 
prev {
[yhat|->f 20]
[zhat|->yhat*yhat*7]
    next{ zhat }
}
\end{lstlisting}
Finally, when evaluating the outer $\prev$, we must {\em reify} the contained substitutions into let statements, yielding
\begin{lstlisting} 
let yhat = f 20 in
let zhat = yhat * yhat * 7 in z
\end{lstlisting}

>>>>

More precisely, when evaluating the \verb|next|, we construct an explicit
substitution $\mathtt{[\hat y\mapsto f~20]}$ binding its old contents to the
fresh variable $\mathtt{\hat y}$. This substitution is placed at the top of the
containing $\prev$ block:
\begin{lstlisting} 
prev {
[yhat|->f 20]
  let x = (next{yhat}, 7) in
  next{prev{#1 x} * prev{#1 x} *  hold{#2 x}}
}
\end{lstlisting}
%As a convention, we render the new variable with a %stylish and fashionable
%hat.  
We proceed with stage~\bbone\ evaluation, which now duplicates the variable
$\mathtt{\hat y}$ rather than the expression \verb|f 20|.
\begin{lstlisting} 
prev {
[yhat|->f 20]
  next{
    prev{#1 (next {yhat}, 7)} * 
    prev{#1 (next {yhat}, 7)} *
    hold{#2 (next {yhat}, 7)}
  }
}
\end{lstlisting}
We then speculate to reduce the projections and cancel the $\next$s and $\prev$s, giving:
\begin{lstlisting} 
prev {
[yhat|->f 20]
    next{ yhat * yhat * 7 }
}
\end{lstlisting}
Once again, we lift the results of speculation into a substitution:
\begin{lstlisting} 
prev {
[yhat|->f 20]
[zhat|->yhat*yhat*7]
    next{ zhat }
}
\end{lstlisting}
Finally, when canceling the last $\next$ and $\prev$, we must {\em reify} the contained substitutions into let statements, yielding
\begin{lstlisting} 
let yhat = f 20 in
let zhat = yhat * yhat * 7 in zhat
\end{lstlisting}
